\thesistitle

### 2019-07-25 sections/research.tex
Example for type 3 threshold

\begin{eqfloat}\label{eq:type3r}
$$\text{T3R Gap Percentage}=\frac{Statements(C_{gap})}{Statements(C_{above} \cup C_{below})}*100$$
$$Statements = \text{The amount of statements in this code fragment}$$
$$C_{gap} = \text{The gap between two clones}$$
$$C_{above} = \text{The clone instance above the gap}$$
$$C_{below} = \text{The clone instance below the gap}$$
\caption{Type 3R clone merge opportunities threshold formula}\end{eqfloat}

>>>>

\begin{equation}\label{eq:type3r}
\text{T3R Gap Size}=\frac{\text{Number of nodes in gap}}{\text{Number of nodes in clones}}*100
\end{equation}

When applying this formula with the example given in figure \ref{fig:gappedclones}, we get a gap size of 25\%:

\begin{equation}\label{eq:type3r}
\text{T3R Gap Size}=\frac{\text{|\{doC()\}|}}{\text{|\{doA(), doB(), doD(), doE()\}|}}*100 = \frac{\text{1}}{\text{4}}*100 = 25\%
\end{equation}

\begin{figure}[H]
\begin{parcolumns}{2}
\colchunk[1]{
\begin{javacode}
public void doStuff(){
|\highlightYellow|  doA(); // Clone instance of
|\highlightYellow|  doB(); // two statements
  doC(); // Gap of one statement
|\highlightBlue|  doD(); // Clone instance of
|\highlightBlue|  doE(); // two statements
}
\end{javacode}}
\colchunk[2]{
\begin{javacode}
public void doStuff(){
|\highlightYellow|  doA(); // Clone instance of
|\highlightYellow|  doB(); // two statements
  doF(); // Gap of one statement
|\highlightBlue|  doD(); // Clone instance of
|\highlightBlue|  doE(); // two statements
}
\end{javacode}}
\end{parcolumns}
\caption{Gapped clones.}
\label{fig:gappedclones}
\end{figure}
